### 2020-03-16 writeup/setup.tex
wip

In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1), (X_2, Y_2), \dots, (X_k, Y_k)$.
We use a shared body (module) $B$ for all tasks and a separate head (module) $\set{A_i}_{i=1}^k$ for each task.
%    \paragraph{Different covariates:}
This corresponds to minimizing the following optimization objective.
\begin{align}
	\label{eq_mtl}
	f(B; A_1, \dots, A_k) = \sum_{i=1}^k \normFro{X_i B A_i - Y_i}^2.
\end{align}
Note that we consider the natural parameterization without reweighting the tasks above.

@@

Our hypothesis is that the heterogeneity among the multiple tasks can be categorized into two classes, \textit{covariate shift} and \textit{model shift}. %\todo{Add some references to add spice on these takes.}

@@

When the models are the same for all tasks, we use a simplified objective as follows.
\begin{align}
	\label{eq_mtl_basic}
	f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2.
\end{align}
%{\bf The distributed learning problem.}
%    \begin{align}
%     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
%   \end{align}

>>>>

In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1), (X_2, Y_2), \dots, (X_k, Y_k)$.
We use a shared body (module) $B$ for all tasks and a separate head (module) $\set{A_i}_{i=1}^k$ for each task.
%    \paragraph{Different covariates:}
This corresponds to minimizing the following optimization objective.
\begin{align}
	\label{eq_mtl}
	f(B; A_1, \dots, A_k) = \sum_{i=1}^k \norm{X_i B A_i - Y_i}^2.
\end{align}
Note that we consider the natural parameterization without reweighting the tasks above.
The shared body $B$ plays an important role because it allows information transfer between different task data.

@@

Our hypothesis is that the heterogeneity among the multiple tasks can be categorized into two classes, \textit{covariate shift} and \textit{model shift}. %\todo{Add some references to add spice on these takes.}
We consider two natural questions within each category.
\begin{itemize}
	\item How does covariate shift affect the rate of information transfer? For example, is it better to have the same covariance matrix or not?
	\item Under model shift, when do we get positive vs. negative transfer? How does the type of transfer depend on the number of data points, the distance of the task models etc?
\end{itemize}

@@

When the models are the same for all tasks, we use a simplified objective as follows.
\begin{align}
	\label{eq_mtl_basic}
	f(w) = \sum_{i=1}^k \norm{X_i w - Y_i}^2.
\end{align}
%{\bf The distributed learning problem.}
%    \begin{align}
%     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
%   \end{align}
